Literature Review

### 2019-03-13 litreview.Rmd
update

*  The challenges of teaching technical writing in the STEM disciplines
*  Needs and barriers for training future faculty to teach technical writing
*  Automated text analysis and classification

Follow the links below (or from top menu) to sub-pages that explore each of these challenges in more detail.

@@

####Challenges of Teaching Technical Writing
More than 50% of colleges and universities use some form of Writing in the Disciplines, Write to Learn, and Writing Across the Curriculum (WID/WTL/WAC) as part of their general education programs. There are well-established WAC/WID teaching principles based on >40 years of evidence and experience, but much of this work focuses on non-technical styles of writing. We know much less about teaching technical writing specifically. What do we know, and what can we bring from the WAC/WID community? What do we NOT know?  
https://adanieljohnson.github.io/default_website/techwriting.html

####Challenges of Training Future Faculty
A major barrier to routine writing in STEM is limited instructor awareness of evidence-based training models. Many college STEM teachers have never been introduced to proven writing training strategies or trained to give effective, context-specific feedback. How does this impact instruction more generally?  
https://adanieljohnson.github.io/default_website/futurefaculty.html

####Challenges of Applying Automated Text Analysis to Student Learning
Interest in technology-assisted automated feedback on writing began in the mid-1960s. Systems have progressed from basic spelling and grammar checkers to automated essay scoring (AES) systems that provide feedback on the content of open-response writing. Can automated text analysis support student learning?  
https://adanieljohnson.github.io/default_website/aacr.html

####Text Classification 1 - Feature Selection and Engineering
What is the general strategy and steps for solving a text classification problem? What features are important? 
https://adanieljohnson.github.io/default_website/Text_Classifier_Models.html

@@

####Text Classification 4 - Evaluating and Improving the Classifier
If there are many ways to classify texts, how do we know which one is most accurate? How can we improve the classification process? How do we make comparisons and evaluate the different steps in a text classification problem?  
https://adanieljohnson.github.io/default_website/Improving_classifier.html

>>>>

*  The challenges of teaching technical writing to students in STEM disciplines
*  Needs and barriers for training future faculty to teach technical writing
*  Automated text analysis and classification

Sub-pages (links below and in top menu) explore each of these challenges in detail.

@@

####Challenges of Teaching Technical Writing
Over 50% of colleges and universities have some form of Writing in the Disciplines, Write to Learn, or Writing Across the Curriculum (WID/WTL/WAC) as part of their general education programs. There are well-established WAC/WID teaching principles for non-technical writing based on >40 years of evidence and experience, but we know much less about teaching technical writing. What do we know, and what can we import from the WAC/WID community? What do we NOT know?  
https://adanieljohnson.github.io/default_website/techwriting.html

####Challenges of Training Future Faculty
One major barrier to incorporating more writing in STEM courses is limited instructor awareness of evidence-based training models. Many college STEM teachers have never been introduced to proven writing training strategies or trained to give effective, context-specific feedback. How does this impact instruction more generally?  
https://adanieljohnson.github.io/default_website/futurefaculty.html

####Challenges of Applying Automated Text Analysis to Student Learning
How well does automated text analysis support student learning? Can it extend what instructors do beyond current capabiities, or does it only replicate what instructors already do? Students claim to want more opportunities for feedback and revision, but do they actually act on automated feedback?  
https://adanieljohnson.github.io/default_website/aacr.html

####Text Classification 1 - Feature Selection and Engineering
What is the general strategy for solving a text classification problem? What features of texts are important?  
https://adanieljohnson.github.io/default_website/Text_Classifier_Models.html

@@

####Text Classification 4 - Evaluating and Improving the Classifier
If there are many ways to classify texts, how do we know which one is most accurate? How can we improve the classification process? How do we make comparisons and evaluate the outcomes of a text classification problem?  
https://adanieljohnson.github.io/default_website/Improving_classifier.html
